### 2014-11-08 src/docs/talks/paris-dauphine-2014/stan-overview.tex
updated talk to remove redundancy and move ode discussion up with funs

\sld{Why? (cont.)}
%
\begin{itemize}
\item {\slshape Problem}:  Need ease of use of BUGS
\item {\slshape Solution}: Compile a domain-specific language
%
\vspace*{8pt}
\item {\slshape Problem}:  Pure directed graphical language inflexible
\item {\slshape Solution}: Imperative probabilistic programming language

\vspace*{8pt}
\item {\slshape Problem}:  Need to tune parameters for HMC
\item {\slshape Solution}: Tune step size and estimate mass matrix
  during warmup;  on-the-fly number of steps (NUTS)
%
\end{itemize}

@@

\sld{Why? (continued)}
\begin{itemize}
\item {\slshape Problem}:  Nobody knows everything
\item {\slshape Solution}: Expand project team with specialists
\vspace*{8pt}
\item {\slshape Problem}:  Nobody knows everything
\item {\slshape Solution}: Expand project team with specialists
\vspace*{8pt}
\item {\slshape Problem}:  Heterogeneous user base
\item {\slshape Solution}: More interfaces (R, Python, MATLAB, Julia),
  domain-specific examples, tutorials

\end{itemize}

\sld{Why? (continued)}
\begin{itemize}
\item {\slshape Problem}:  Expanding project team and interfaces
\item {\slshape Solution}: GitHub process: branch, pull request, code
  review, continuous integration
%
\vspace*{8pt}
\item {\slshape Problem}:  Restrictive licensing (e.g., closed, GPL, etc.)
\item {\slshape Solution}: Open-source, BSD license
\end{itemize}

>>>>

\sld{Why? (cont.)}
%
\begin{itemize}
\item {\slshape Problem}:  Need ease of use of BUGS
\item {\slshape Solution}: Compile a domain-specific language
%
\vspace*{8pt}
\item {\slshape Problem}:  Pure directed graphical language inflexible
\item {\slshape Solution}: Imperative probabilistic programming
  language
\vspace*{8pt}
\item {\slshape Problem}:  Need to tune parameters for HMC
\item {\slshape Solution}: Tune step size and estimate mass matrix
  during warmup;  on-the-fly number of steps (NUTS)
%
\end{itemize}

@@

\sld{Why? (continued)}
\begin{itemize}
\item {\slshape Problem}:  Nobody knows everything
\item {\slshape Solution}: Expand project team with specialists
\vspace*{8pt}
\item {\slshape Problem}:  Expanding code and project team
\item {\slshape Solution}: GitHub: branch, pull 
  request, code review
\item {\slshape Solution}: Jenkins: continuous integration
\item {\slshape Solution}: ongoing refactoring and code simplification
%
\end{itemize}

\sld{Why? (continued)}
\begin{itemize}
\item {\slshape Problem}:  Heterogeneous user base
\item {\slshape Solution}: More interfaces (R, Python, MATLAB, Julia)
\item {\slshape Solution}:  domain-specific examples, tutorials
\vspace*{8pt}
\item {\slshape Problem}:  Restrictive licensing limits use
\item {\slshape Solution}: Code and doc open source
(BSD, CC-BY)
\end{itemize}
